An Open-Source Implementation of the CMPS Algorithm for Assessing  Similarity of Bullets

### 2021-09-10 CMPSpaper_writing/CMPSpaper_writing.Rmd
fig 11 + 13

bibliography: CMPSpaper-writing.bib
output: rticles::rjournal_article
editor_options: 
  chunk_output_type: inline
---

```{=tex}
\newcommand{\hh}[1]{{\textcolor{orange}{#1}}}
\newcommand{\wj}[1]{{\textcolor{blue}{#1}}}
\setlength{\parindent}{0pt}
```

\hh{Still to add: the CMPS diff measure, in which you subtract the background. 
A comparison to results from bulletxtrctr's random forest.}
\hh{The random forest is spitting out results on a [0-1] interval - so we might need to compare to the adjusted measure. That comarison should go into a separate section just before the discussion. Like - comparison to other existing methods ... special request from Alicia :)}

```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(knitr)
library(tidyverse)
library(bulletxtrctr)
library(knitr)
library(kableExtra)

@@

A report published by @nrc states that "[m]uch forensic evidence-including, for example, bite marks and firearm and toolmark identification—is introduced in criminal trials without any meaningful scientific validation, determination of error rates, or reliability testing to explain the limits of the discipline." To overcome those criticisms and concerns, researchers have been making an effort to build databases and develop frameworks and algorithms that bring an objective and quantitative assessment into the field [@nistdb, @brundage, @hamby, @Hamby:2019, @song2005, @ChumbleyL_Scott2010VoTM, @aoas, @pmid30444940;@cmps]. Note that this is not an exhaustive list of these efforts. The notion of bullet signatures is one of the results of these efforts. Bullet signatures can be extracted from bullet land engraved areas (LEAs), typically one for each land engraved area, and how those bullet signatures are extracted from scans will be discussed in the Background section. Since bullet signatures can numerically describe the striation marks on the bullet and can be understood by algorithms, they played an important role in bringing objectivity into the field. 
In the following sections we will: review the background of bullet signature comparisons, discuss how we followed the idea described by @cmps for the implementation of the CMPS algorithm, and present results of applying our implementation to real data.

@@

The datasets we worked with come from the James Hamby Consecutively Rifled Ruger Barrel Study [@brundage; @hamby; @Hamby:2019],  in particular, Hamby set 252 and Hamby set 44. 
For each Hamby set, a total of 35 bullets is fired from ten consecutively manufactured Ruger P-85 pistol barrels. Two bullets are fired from each barrel, making up a set of 20 reference bullets. An additional 15 bullets are fired from these ten barrels in a fashion unknown to the study participant. The aim of the Hamby Study was to have firearms examiners identify which barrel each of the 15 questioned bullets was fired from. The Ruger P-85 barrels are traditionally rifled barrels with six grooves and lands as shown in \autoref{fig:bullet}. During the firing process, grooves and lands are engraved on a bullet. Firearms examiners use striation marks on land engraved areas (LEAs) for their visual comparison. For algorithmic purposes, 
3D topographical images of land engraved areas were obtained and stored in  x3p format (XML 3-D Surface Profile). The x3p format provides a standard way of exchanging 2D and 3D profile data. It conforms to the ISO5436-2 standard [http://sourceforge.net/p/open-gps/mwiki/X3p/]  adopted by the OpenFMC (Open Forensic Metrology Consortium), a group of firearm forensics researchers who contributes to the establishment of best practices of using metrology in forensic science. Hamby set 252 were scanned using a NanoFocus lens at 20x magnification with the scan resolution being 1.5625 \textmu m $\times$ 1.5625 \textmu m per pixel. Hamby set 44 was scanned at the Roy J Carver High-Resolution microscopy lab at Iowa State. These scans were acquired with a Sensofar Confocal Light Microscope at 20x magnification for a nominal resolution of 0.645 \textmu m $\times$ 0.645 \textmu m per pixel.  Both Hamby set 252 and Hamby set 44 are publicly available on the NIST Ballistics Database Project [@nistdb].

@@

### Conceptual idea of CMPS
Most algorithms for comparing striation marks are based on the digitized signatures and produce a similarity score [@song2005, @ChumbleyL_Scott2010VoTM, @aoas, @pmid30444940 ].
 The congruent matching profile segments (CMPS) algorithm, developed by @cmps for "objective comparison of striated tool marks", is one such algorithm. The algorithm's main idea  is to take a set of consecutive and non-overlapping basis segments from  the comparison  and  for each segment find the "best" registration position on the reference  (the other bullet signature) with respect to their cross-correlation values. From a comparison of these registration positions, a **congruent registration position** is identified, and the number of basis segments taking the congruent registration position is the CMPS score. Note that researchers in @cmps refers the origin of basis segments as the reference, but in this paper we refer it as the comparison.
  High CMPS scores are achieved between more similar signatures and are therefore indicative of a same-source pair. Low scores between pairs of signatures are attributed to different source pairs.
However, a specific threshold of the CMPS score to distinguish between same-source and different-source comparisons is not mentioned in @cmps and depends on the underlying structure of the data and the choice of parameters. Further research is needed to understand how to determine the threshold.
  <!-- \hh{XXX What threshold did @cmps identify as the boundary between different source and same source? And what was the error rate in their example?} -->
  <!-- \wj{they didn't talk about a specific threshold or error rates} \hh{XXX Is there a way to infer the error based on the example? ... 'while the authors did not mention a specific threshold of the CMPS to distinguish between same-source and different-source comparison, a CMPS value of Y results in an error rate of Z in the example.'} -->
 The CMPS algorithm can assist firearm examiners with drawing a conclusion about the source of a comparison pair. Unfortunately, @cmps did not release any code or specific parameter settings for their implementation of the CMPS algorithm. 
Thus, in this paper we present an open-source implementation of the CMPS algorithm in the R package CMPS available from Github \url{https://github.com/willju-wangqian/CMPS}
With our implementation, one can compute the CMPS score of a comparison using the following code:

@@

    + **Calculate the cross-correlation curve:**  Calculate the cross-correlation curve between a basis segment `x` and the reference signature `y` using the function `get_ccf4(x, y, ...)` as shown in \autoref{fig:segplot2}. The position indicates the lag by which a basis segment is moved with respect to its original placement. A position is considered "good" if it results in a peak in the cross-correlation between the basis segment and the reference.
    + **Correlation peaks:** Two strategies referred to as "multi-peak inspection" and "multi-peak inspection at different segment lengths" in @cmps are used for identifying positions of correlation peaks as candidate positions. The latter is also called "multi-segment lengths strategy". The parameter `npeaks.set` in `extract_feature_cmps(...)` determines which strategy to use and the number of candidate positions: 
        -   If `npeaks.set` is an integer vector of length 1, for example `npeaks.set = 5`, the positions of the top five peaks in the cross-correlation curve are identified as candidate positions for registration. 
        -   If `npeaks.set` is an integer vector of length more than 1, for example `npeaks.set = c(5, 3, 1)`, the multi-segment lengths strategy will be used: calculate the cross-correlation function between a basis segment and the reference and identify positions of the top five peaks; double the segment length to a specified value, re-calculate the cross-correlation function, and identify three peaks; repeat this process and identify a single peak in the newly computed cross-correlation function. \autoref{fig:seg_all} shows an example of three levels of basis segment 6 and their corresponding cross-correlation curves and identified peaks. Note that in @cmps the segment length is doubled at each level of a basis segment, but in the present implementation users are allowed to choose the segment length at each level.
        -   `get_ccr_peaks(comp, segments, seg_outlength, nseg = 1, npeaks = 5)` computes the cross-correlation curve between a basis or increased segment and the reference signature and finds peaks in the cross-correlation curve. The number of peaks detected is equal to `npeaks`, which is an integer. `segments`, `seg_outlength`, and `nseg` determines the segment in the cross-correlation computation, and `comp` gives the reference signature. If the multi-segment lengths strategy is used, then `get_ccr_peaks(...)` is called in a `lapply()` for each level of the basis segment. The resulting list is called `ccr.list`.
    +  **multi-segment lengths strategy:** with the multi-segment lengths strategy being used, a position is identified as a candidate position for registration and is called as a "consistent correlation peak" if it results in a top peak in the cross-correlation curve with a tolerance zone determined by `Tx` in all segment levels. Note that in @cmps, a segment at its largest scale (highest level) always identifies one peak, but we do not have this requirement in our implementation.
        -   the function `get_seg_scale(segments, nseg, out_length)` is used to obtain the (potentially increased) version of a basis segment. `segments`, which is a list containing all basis segments generated by the function `get_segs(...)` in step 1, and `nseg` are used to determine the basis segment to be increased. `out_length` specifies the length of the output segment.
        -   `get_ccp(ccr.list, Tx = 25)` tries to identify the "consistent correlation peak". `ccr.list` is the result of `lapply()` and `get_ccr_peaks(...)`, and `Tx` determines the size of a tolerance zone used in identifying the consistent correlation peak. `get_ccp(...)` returns `NULL` if there is no consistent correlation peak.

@@

* `x` and `y` are  two  signatures:  `x` serves as the comparison signature (which will be divided into basis segments) and `y` is the reference signature;

* `include` determines the format of the function result. Besides the `CMPS.score`, other aspects of the comparison help in understanding how the `CMPS.score` is computed. By default `include` is set to `NULL` and  only  the `CMPS.score` is returned; further results are included when `include` is (an abbreviation of) one of or a vector of the following strings: `"nseg", "congruent.pos", "congruent.seg.idx", "segments", "parameters"`, and `"full_result"`. If `include` is specified as `"full_result"` (or its abbreviation), the output includes everything listed below.
  - `nseg`: the number of basis segments  from the comparison signature; this is also the highest possible CMPS score of the comparison;
  - `congruent.pos`: the congruent registration position;
  - `congruent.seg.idx`: the indices of all congruent matching profile segments;
  - `ccp.list`: a list showing identified candidate positions of all basis segments; 
  - `pos.df`: a data frame containing all candidate positions and their respective number of votes;
  - `segments`: a list containing all basis segments;
  - `parameters`: a list containing all input arguments of `extract_feature_cmps`;

* `outlength` specifies the segment length of a basis segment at each level under the multi-segment lengths strategy. By default `outlength` is set to `NULL`, indicating that a basis segment should double its segment length at the next level and conforming to the description in @cmps .

@@

<!-- [examples https://journal.r-project.org/archive/2019/RJ-2019-044/RJ-2019-044.pdf] -->
<!-- [https://journal.r-project.org/archive/2019/RJ-2019-002/RJ-2019-002.pdf] -->

@@

<!-- ```{r, eval=FALSE} -->
<!-- install.packages("CMPS") -->
<!-- ``` -->

@@

*   The first element is a plot called `segment_shift_plot`, shown in \autoref{fig:sigplot}. On this plot the reference signature is drawn as a black line,  congruent matching profile segments from the comparison signature are overlaid in red at the congruent registration position.

@@

*   The second plot is called `signature_shift_plot`, shown in \autoref{fig:sigplot2}. This visual presents both the comparison signature and the reference signature. The comparison signature is aligned with the reference signature based on the congruent registration position. Congruent matching profile segments are highlighted by  solid red lines.

\begin{figure}[hbt]
\begin{subfigure}[t]{\textwidth}
\caption{\label{fig:sigplot}The black line shows the comparison signature; each red line segment shows one congruent matching profile segment.}
```{r sigplot, opts.label="codefig", echo=TRUE, out.width='\\textwidth', warning = FALSE}
sig.plot <- cmps_signature_plot(
  cmps_with_multi_scale
)
sig.plot$segment_shift_plot
```
\end{subfigure}
\begin{subfigure}[t]{\textwidth}
\caption{\label{fig:sigplot2}The black line shows the reference signature; the red line shows the comparison signature. Solid part shows the congruent matching profile segments, and the dashed part shows segments that do not agree with the congruent registration position.}
```{r sigplot2, opts.label="codefig", echo=TRUE, out.width='\\textwidth', warning = FALSE}
sig.plot$signature_shift_plot
```
\end{subfigure}
\caption{\label{fig:sigplots} Two visual outputs of cmps\_signature\_plot()}
\end{figure}

*   Other elements of this list are `seg_shift` and `sig_shift`. `sig_shift` gives the congruent registration position, while `seg_shift` is a data frame showing the congruent matching profile segments and their identified candidate position closest to the congruent registration position.

@@

<!-- These elements are essentially used for generating visuals above but also provide insights about the congruent registration position and the candidate positions found by each of the congruent matching profile segments.  -->
<!-- which basis segments are the congruent matching profile segments. -->

@@

*   \autoref{fig:segplot} is the `segment_plot` for basis segment 6 at level one (in its original length). We used  `npeaks.set = c(5, 3, 1)` in `extract_feature_cmps()` when calculating the CMPS score. Therefore the top five peaks are identified in the cross-correlation curve at level one. Segment 6 is plotted at the positions where these 5 peaks are identified with dashed lines in the `segment_plot`. The solid thick black line shows the segment at its original position (which in this example is very close to the actual registration position). 
*   \autoref{fig:segplot2} is the `scale_ccf_plot` of basis segment 6 at level one. It shows the cross-correlation curve computed by the reference signature and the level-one basis segment 6. The five highest peaks are marked by dots on the curve.

\begin{figure}
\begin{subfigure}[t]{\textwidth}
\caption{\label{fig:segplot}segment\_plot for segment 6 at level one. The original position of segment 6 is indicated by the solid black line. Positions where the segment achieves the 5 highest cross-correlations are indicated by the dashed line segments.}
```{r segplot, opts.label="codefig", echo=TRUE, out.width='\\textwidth', warning = FALSE}
seg.plot <- cmps_segment_plot(
  cmps_with_multi_scale, 
  seg.idx = 6
)
seg.plot[[1]]$segment_plot
```
\end{subfigure}
\begin{subfigure}[t]{\textwidth}
\caption{\label{fig:segplot2}scale\_ccf\_plot shows the cross-correlation curve between the reference signature and segment 6 at level one. The five highest peaks are marked by dots. The vertical red dashed line indicates the congruent registration position; the green dashed line shows a peak position in the highest segment level; the blue dashed lines show the tolerance zone around the green dashed line. We can see that none of the five highest peaks at level one falls within the tolerance zone, indicating that there is no consistent correlation peak or a candidate position identified by basis segment 6 under the multi-segment lengths strategy. Thus, the basis segment 6 doesn't vote for the congruent registration position and is not a cmps.}
```{r segplot2, opts.label="codefig", echo=TRUE, out.width='\\textwidth', warning = FALSE}
seg.plot[[1]]$scale_ccf_plot
```
\end{subfigure}
\caption{\label{fig:segplots} Two plots used to investigate basis segment 6 at level one}
\end{figure}

Additionally, users can have more insights about why segment 6 is not a congruent matching profile segment if we put the `segment_plot` and `scale_ccf_plot` of all three segment levels together, as shown in \autoref{fig:seg_all} with the help of `ggpubr::ggarrange()`.

\begin{figure}
```{r segplot3, opts.label="codefig", echo=TRUE, out.width='\\textwidth', warning = FALSE}
library(ggpubr)

ggarrange(
  plotlist = 
    unlist(seg.plot, 
           recursive = FALSE),
  ncol = 2, 
  nrow = 3)
```
\caption{\label{fig:seg_all} Put segment\_plot and scale\_ccf\_plot of all three levels together. We are identifying five highest peaks at level one, three peaks at level two, and one peak at level three since npeaks.set = c(5, 3, 1). The highest peak position at level three is marked by the green dashed line across all segment levels. However, the highest peak on level three does not coincide with any of the top five highest peaks at level one. This indicates that there is no consistent correlation peak or a candidate position for basis segment 6 under the multi-segment lengths strategy.}
\end{figure}

In \autoref{fig:seg_all}, the red vertical dashed line indicates the congruent registration position. We can see that the basis segment 6 does obtain a peak near the congruent registration position at level two and level three, respectively; however, this position doesn't give one of the five highest peaks at level one. As a result, segment 6 fails to identify the consistent correlation peak (ccp) and fails to become one of the congruent matching profile segments according to the multi-segment lengths strategy. The identified top five peaks at level one are also examples of "false positive" peaks. The "true positive" peak (the peak within the tolerance zone of the congruent registration position) is identified at level two and three by increasing the segment length, which justifies the usage of multi-segment lengths strategy.

@@

\begin{align}
\mathrm{CMPS_{max}} &= \max_{i,j} c_{ij} \text{ , and} \\
\mathrm{\overline{CMPS}_{max}} &= \frac{1}{n} \sum_{(i,j) \in \mathcal{P}_{k^*}} c_{ij} \text{ , where} \\
k^* &= \text{arg}\max\limits_{k} \left[  \frac{1}{n} \sum_{(i,j) \in \mathcal{P}_k} c_{ij}\right]
\end{align}

<!-- \begin{align} -->
<!-- \mathrm{CMPS_{max}} &= \max_{i,j} c_{ij}, \text{and }\\ -->
<!-- \mathrm{\overline{CMPS}_{max}} &= \max_{k} \left[  \frac{1}{n} \sum_{(i,j) \in \mathcal{P}_k} c_{ij}\right]. -->
<!-- \end{align} -->
<!-- \hh{XXX point out that neither of these measures evaluates the non-matches, and introduce CMPS diff here} -->

@@

\begin{align}
\mathrm{\overline{CMPS}_{diff}} = \left[  \frac{1}{n} \sum_{(i,j) \in \mathcal{P}_{k^*}} c_{ij}\right] - \left[  \frac{1}{n(n-1)} \sum_{(i,j) \notin \mathcal{P}_{k^*}} c_{ij}\right]
\end{align}

$\mathrm{\overline{CMPS}_{diff}}$ highlights the difference between CMPS scores of matching and non-matching comparisons. If two bullets are non-matching, all 36 CMPS scores are expected to be small with relatively the same values, resulting in a $\mathrm{\overline{CMPS}_{diff}}$ value close to 0. For the example above, $\mathrm{\overline{CMPS}_{diff}} = 12.5 - 1.53 = 10.97$ <br>

@@

\begin{align}
y_{kl} = \mu_k + e_{kl}
\end{align}

where $\mu_k$ is the true mean of group $k$ and $e_{kl}$ is a random effect of different observations. Then we can define the sum of squares ratio $V$ as:

\begin{align}
V = \frac{\sum_k n_k (\bar{y}_{k.} - \bar{y}_{..})^2}{\sum_k \sum_l^{n_k} (y_{kl} - \bar{y}_{k.})^2 }.
\end{align}

>>>>

bibliography: CMPSpaper-writing.bib
output: rticles::rjournal_article
editor_options: 
  chunk_output_type: inline
  markdown: 
    wrap: sentence
---

```{=tex}
\newcommand{\hh}[1]{{\textcolor{orange}{#1}}}
\newcommand{\wj}[1]{{\textcolor{blue}{#1}}}
\setlength{\parindent}{0pt}
```
```{=tex}
\hh{Still to add: the CMPS diff measure, in which you subtract the background. 
A comparison to results from bulletxtrctr's random forest.}
\hh{The random forest is spitting out results on a [0-1] interval - so we might need to compare to the adjusted measure. That comarison should go into a separate section just before the discussion. Like - comparison to other existing methods ... special request from Alicia :)}
```
```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(knitr)
library(tidyverse)
library(bulletxtrctr)
library(knitr)
library(kableExtra)
library(patchwork)

@@

A report published by @nrc states that "[m]uch forensic evidence-including, for example, bite marks and firearm and toolmark identification---is introduced in criminal trials without any meaningful scientific validation, determination of error rates, or reliability testing to explain the limits of the discipline." To overcome those criticisms and concerns, researchers have been making an effort to build databases and develop frameworks and algorithms that bring an objective and quantitative assessment into the field [@nistdb, @brundage, @hamby, @Hamby:2019, @song2005, @ChumbleyL_Scott2010VoTM, @aoas, @pmid30444940; @cmps].
Note that this is not an exhaustive list of these efforts.
The notion of bullet signatures is one of the results of these efforts.
Bullet signatures can be extracted from bullet land engraved areas (LEAs), typically one for each land engraved area, and how those bullet signatures are extracted from scans will be discussed in the Background section.
Since bullet signatures can numerically describe the striation marks on the bullet and can be understood by algorithms, they played an important role in bringing objectivity into the field.
In the following sections we will: review the background of bullet signature comparisons, discuss how we followed the idea described by @cmps for the implementation of the CMPS algorithm, and present results of applying our implementation to real data.

@@

The datasets we worked with come from the James Hamby Consecutively Rifled Ruger Barrel Study [@brundage; @hamby; @Hamby:2019], in particular, Hamby set 252 and Hamby set 44.
For each Hamby set, a total of 35 bullets is fired from ten consecutively manufactured Ruger P-85 pistol barrels.
Two bullets are fired from each barrel, making up a set of 20 reference bullets.
An additional 15 bullets are fired from these ten barrels in a fashion unknown to the study participant.
The aim of the Hamby Study was to have firearms examiners identify which barrel each of the 15 questioned bullets was fired from.
The Ruger P-85 barrels are traditionally rifled barrels with six grooves and lands as shown in \autoref{fig:bullet}.
During the firing process, grooves and lands are engraved on a bullet.
Firearms examiners use striation marks on land engraved areas (LEAs) for their visual comparison.
For algorithmic purposes, 3D topographical images of land engraved areas were obtained and stored in x3p format (XML 3-D Surface Profile).
The x3p format provides a standard way of exchanging 2D and 3D profile data.
It conforms to the ISO5436-2 standard [<http://sourceforge.net/p/open-gps/mwiki/X3p/>] adopted by the OpenFMC (Open Forensic Metrology Consortium), a group of firearm forensics researchers who contributes to the establishment of best practices of using metrology in forensic science.
Hamby set 252 were scanned using a NanoFocus lens at 20x magnification with the scan resolution being 1.5625 \textmu m $\times$ 1.5625 \textmu m per pixel.
Hamby set 44 was scanned at the Roy J Carver High-Resolution microscopy lab at Iowa State.
These scans were acquired with a Sensofar Confocal Light Microscope at 20x magnification for a nominal resolution of 0.645 \textmu m $\times$ 0.645 \textmu m per pixel.
Both Hamby set 252 and Hamby set 44 are publicly available on the NIST Ballistics Database Project [@nistdb].

@@

### Conceptual idea of CMPS

Most algorithms for comparing striation marks are based on the digitized signatures and produce a similarity score [@song2005, @ChumbleyL_Scott2010VoTM, @aoas, @pmid30444940].
The congruent matching profile segments (CMPS) algorithm, developed by @cmps for "objective comparison of striated tool marks", is one such algorithm.
The algorithm's main idea is to take a set of consecutive and non-overlapping basis segments from the comparison and for each segment find the "best" registration position on the reference (the other bullet signature) with respect to their cross-correlation values.
From a comparison of these registration positions, a **congruent registration position** is identified, and the number of basis segments taking the congruent registration position is the CMPS score.
Note that researchers in @cmps refers the origin of basis segments as the reference, but in this paper we refer it as the comparison.
High CMPS scores are achieved between more similar signatures and are therefore indicative of a same-source pair.
Low scores between pairs of signatures are attributed to different source pairs.
However, a specific threshold of the CMPS score to distinguish between same-source and different-source comparisons is not mentioned in @cmps and depends on the underlying structure of the data and the choice of parameters.
Further research is needed to understand how to determine the threshold.
<!-- \hh{XXX What threshold did @cmps identify as the boundary between different source and same source? And what was the error rate in their example?} --> <!-- \wj{they didn't talk about a specific threshold or error rates} \hh{XXX Is there a way to infer the error based on the example? ... 'while the authors did not mention a specific threshold of the CMPS to distinguish between same-source and different-source comparison, a CMPS value of Y results in an error rate of Z in the example.'} --> The CMPS algorithm can assist firearm examiners with drawing a conclusion about the source of a comparison pair.
Unfortunately, @cmps did not release any code or specific parameter settings for their implementation of the CMPS algorithm.
Thus, in this paper we present an open-source implementation of the CMPS algorithm in the R package CMPS available from Github \url{https://github.com/willju-wangqian/CMPS} With our implementation, one can compute the CMPS score of a comparison using the following code:

@@

    -   **Calculate the cross-correlation curve:** Calculate the cross-correlation curve between a basis segment `x` and the reference signature `y` using the function `get_ccf4(x, y, ...)` as shown in \autoref{fig:segplot2}. The position indicates the lag by which a basis segment is moved with respect to its original placement. A position is considered "good" if it results in a peak in the cross-correlation between the basis segment and the reference.

    -   **Correlation peaks:** Two strategies referred to as "multi-peak inspection" and "multi-peak inspection at different segment lengths" in @cmps are used for identifying positions of correlation peaks as candidate positions. The latter is also called "multi-segment lengths strategy". The parameter `npeaks.set` in `extract_feature_cmps(...)` determines which strategy to use and the number of candidate positions:

        -   If `npeaks.set` is an integer vector of length 1, for example `npeaks.set = 5`, the positions of the top five peaks in the cross-correlation curve are identified as candidate positions for registration.
        -   If `npeaks.set` is an integer vector of length more than 1, for example `npeaks.set = c(5, 3, 1)`, the multi-segment lengths strategy will be used: calculate the cross-correlation function between a basis segment and the reference and identify positions of the top five peaks; double the segment length to a specified value, re-calculate the cross-correlation function, and identify three peaks; repeat this process and identify a single peak in the newly computed cross-correlation function. \autoref{fig:seg_all} shows an example of three levels of basis segment 6 and their corresponding cross-correlation curves and identified peaks. Note that in @cmps the segment length is doubled at each level of a basis segment, but in the present implementation users are allowed to choose the segment length at each level.
        -   `get_ccr_peaks(comp, segments, seg_outlength, nseg = 1, npeaks = 5)` computes the cross-correlation curve between a basis or increased segment and the reference signature and finds peaks in the cross-correlation curve. The number of peaks detected is equal to `npeaks`, which is an integer. `segments`, `seg_outlength`, and `nseg` determines the segment in the cross-correlation computation, and `comp` gives the reference signature. If the multi-segment lengths strategy is used, then `get_ccr_peaks(...)` is called in a `lapply()` for each level of the basis segment. The resulting list is called `ccr.list`.

    -   **multi-segment lengths strategy:** with the multi-segment lengths strategy being used, a position is identified as a candidate position for registration and is called as a "consistent correlation peak" if it results in a top peak in the cross-correlation curve with a tolerance zone determined by `Tx` in all segment levels. Note that in @cmps, a segment at its largest scale (highest level) always identifies one peak, but we do not have this requirement in our implementation.

        -   the function `get_seg_scale(segments, nseg, out_length)` is used to obtain the (potentially increased) version of a basis segment. `segments`, which is a list containing all basis segments generated by the function `get_segs(...)` in step 1, and `nseg` are used to determine the basis segment to be increased. `out_length` specifies the length of the output segment.
        -   `get_ccp(ccr.list, Tx = 25)` tries to identify the "consistent correlation peak". `ccr.list` is the result of `lapply()` and `get_ccr_peaks(...)`, and `Tx` determines the size of a tolerance zone used in identifying the consistent correlation peak. `get_ccp(...)` returns `NULL` if there is no consistent correlation peak.

@@

-   `x` and `y` are two signatures: `x` serves as the comparison signature (which will be divided into basis segments) and `y` is the reference signature;

-   `include` determines the format of the function result.
    Besides the `CMPS.score`, other aspects of the comparison help in understanding how the `CMPS.score` is computed.
    By default `include` is set to `NULL` and only the `CMPS.score` is returned; further results are included when `include` is (an abbreviation of) one of or a vector of the following strings: `"nseg", "congruent.pos", "congruent.seg.idx", "segments", "parameters"`, and `"full_result"`.
    If `include` is specified as `"full_result"` (or its abbreviation), the output includes everything listed below.

    -   `nseg`: the number of basis segments from the comparison signature; this is also the highest possible CMPS score of the comparison;
    -   `congruent.pos`: the congruent registration position;
    -   `congruent.seg.idx`: the indices of all congruent matching profile segments;
    -   `ccp.list`: a list showing identified candidate positions of all basis segments;
    -   `pos.df`: a data frame containing all candidate positions and their respective number of votes;
    -   `segments`: a list containing all basis segments;
    -   `parameters`: a list containing all input arguments of `extract_feature_cmps`;

-   `outlength` specifies the segment length of a basis segment at each level under the multi-segment lengths strategy.
    By default `outlength` is set to `NULL`, indicating that a basis segment should double its segment length at the next level and conforming to the description in @cmps .

@@

<!-- [examples https://journal.r-project.org/archive/2019/RJ-2019-044/RJ-2019-044.pdf] -->

<!-- [https://journal.r-project.org/archive/2019/RJ-2019-002/RJ-2019-002.pdf] -->

@@

<!-- ```{r, eval=FALSE} -->

<!-- install.packages("CMPS") -->

<!-- ``` -->

@@

-   The first element is a plot called `segment_shift_plot`, shown in \autoref{fig:sigplot}. On this plot the reference signature is drawn as a black line, congruent matching profile segments from the comparison signature are overlaid in red at the congruent registration position.

@@

-   The second plot is called `signature_shift_plot`, shown in \autoref{fig:sigplot2}. This visual presents both the comparison signature and the reference signature. The comparison signature is aligned with the reference signature based on the congruent registration position. Congruent matching profile segments are highlighted by solid red lines.

```{=tex}
\begin{figure}[hbt]
\begin{subfigure}[t]{\textwidth}
\caption{\label{fig:sigplot}The black line shows the comparison signature; each red line segment shows one congruent matching profile segment.}
```{r sigplot, opts.label="codefig", echo=TRUE, out.width='\\textwidth', warning = FALSE}
sig.plot <- cmps_signature_plot(
  cmps_with_multi_scale
)
sig.plot$segment_shift_plot
```
\end{subfigure}
\begin{subfigure}[t]{\textwidth}
\caption{\label{fig:sigplot2}The black line shows the reference signature; the red line shows the comparison signature. Solid part shows the congruent matching profile segments, and the dashed part shows segments that do not agree with the congruent registration position.}
```{r sigplot2, opts.label="codefig", echo=TRUE, out.width='\\textwidth', warning = FALSE}
sig.plot$signature_shift_plot
```
\end{subfigure}
\caption{\label{fig:sigplots} Two visual outputs of cmps\_signature\_plot()}
\end{figure}
```
-   Other elements of this list are `seg_shift` and `sig_shift`. `sig_shift` gives the congruent registration position, while `seg_shift` is a data frame showing the congruent matching profile segments and their identified candidate position closest to the congruent registration position.

@@

<!-- These elements are essentially used for generating visuals above but also provide insights about the congruent registration position and the candidate positions found by each of the congruent matching profile segments.  -->

<!-- which basis segments are the congruent matching profile segments. -->

@@

-   \autoref{fig:segplot} is the `segment_plot` for basis segment 6 at level one (in its original length). We used `npeaks.set = c(5, 3, 1)` in `extract_feature_cmps()` when calculating the CMPS score. Therefore the top five peaks are identified in the cross-correlation curve at level one. Segment 6 is plotted at the positions where these 5 peaks are identified with dashed lines in the `segment_plot`. The solid thick black line shows the segment at its original position (which in this example is very close to the actual registration position).
-   \autoref{fig:segplot2} is the `scale_ccf_plot` of basis segment 6 at level one. It shows the cross-correlation curve computed by the reference signature and the level-one basis segment 6. The five highest peaks are marked by dots on the curve.

```{=tex}
\begin{figure}
\begin{subfigure}[t]{\textwidth}
\caption{\label{fig:segplot}segment\_plot for segment 6 at level one. The original position of segment 6 is indicated by the solid black line. Positions where the segment achieves the 5 highest cross-correlations are indicated by the dashed line segments.}
```{r segplot, opts.label="codefig", echo=TRUE, out.width='\\textwidth', warning = FALSE}
seg.plot <- cmps_segment_plot(
  cmps_with_multi_scale, 
  seg.idx = 6
)
seg.plot[[1]]$segment_plot
```
\end{subfigure}
\begin{subfigure}[t]{\textwidth}
\caption{\label{fig:segplot2}scale\_ccf\_plot shows the cross-correlation curve between the reference signature and segment 6 at level one. The five highest peaks are marked by dots. The vertical red dashed line indicates the congruent registration position; the green dashed line shows a peak position in the highest segment level; the blue dashed lines show the tolerance zone around the green dashed line. We can see that none of the five highest peaks at level one falls within the tolerance zone, indicating that there is no consistent correlation peak or a candidate position identified by basis segment 6 under the multi-segment lengths strategy. Thus, the basis segment 6 doesn't vote for the congruent registration position and is not a cmps.}
```{r segplot2, opts.label="codefig", echo=TRUE, out.width='\\textwidth', warning = FALSE}
seg.plot[[1]]$scale_ccf_plot
```
\end{subfigure}
\caption{\label{fig:segplots} Two plots used to investigate basis segment 6 at level one}
\end{figure}
```
Additionally, users can have more insights about why segment 6 is not a congruent matching profile segment if we put the `segment_plot` and `scale_ccf_plot` of all three segment levels together, as shown in \autoref{fig:seg_all} with the help of `ggpubr::ggarrange()`.

```{=tex}
\begin{figure}
```{r segplot3, opts.label="codefig", echo=TRUE, out.width='\\textwidth', warning = FALSE}
library(ggpubr)

ggarrange(
  plotlist = 
    unlist(seg.plot, 
           recursive = FALSE),
  ncol = 2, 
  nrow = 3)
```
\caption{\label{fig:seg_all} Put segment\_plot and scale\_ccf\_plot of all three levels together. We are identifying five highest peaks at level one, three peaks at level two, and one peak at level three since npeaks.set = c(5, 3, 1). The highest peak position at level three is marked by the green dashed line across all segment levels. However, the highest peak on level three does not coincide with any of the top five highest peaks at level one. This indicates that there is no consistent correlation peak or a candidate position for basis segment 6 under the multi-segment lengths strategy.}
\end{figure}
```
In \autoref{fig:seg_all}, the red vertical dashed line indicates the congruent registration position.
We can see that the basis segment 6 does obtain a peak near the congruent registration position at level two and level three, respectively; however, this position doesn't give one of the five highest peaks at level one.
As a result, segment 6 fails to identify the consistent correlation peak (ccp) and fails to become one of the congruent matching profile segments according to the multi-segment lengths strategy.
The identified top five peaks at level one are also examples of "false positive" peaks.
The "true positive" peak (the peak within the tolerance zone of the congruent registration position) is identified at level two and three by increasing the segment length, which justifies the usage of multi-segment lengths strategy.

@@

```{=tex}
\begin{align}
\mathrm{CMPS_{max}} &= \max_{i,j} c_{ij} \text{ , and} \\
\mathrm{\overline{CMPS}_{max}} &= \frac{1}{n} \sum_{(i,j) \in \mathcal{P}_{k^*}} c_{ij} \text{ , where} \\
k^* &= \text{arg}\max\limits_{k} \left[  \frac{1}{n} \sum_{(i,j) \in \mathcal{P}_k} c_{ij}\right]
\end{align}
```
<!-- \begin{align} -->

<!-- \mathrm{CMPS_{max}} &= \max_{i,j} c_{ij}, \text{and }\\ -->

<!-- \mathrm{\overline{CMPS}_{max}} &= \max_{k} \left[  \frac{1}{n} \sum_{(i,j) \in \mathcal{P}_k} c_{ij}\right]. -->

<!-- \end{align} -->

<!-- \hh{XXX point out that neither of these measures evaluates the non-matches, and introduce CMPS diff here} -->

@@

```{=tex}
\begin{align}
\mathrm{\overline{CMPS}_{diff}} = \left[  \frac{1}{n} \sum_{(i,j) \in \mathcal{P}_{k^*}} c_{ij}\right] - \left[  \frac{1}{n(n-1)} \sum_{(i,j) \notin \mathcal{P}_{k^*}} c_{ij}\right]
\end{align}
```
$\mathrm{\overline{CMPS}_{diff}}$ highlights the difference between CMPS scores of matching and non-matching comparisons.
If two bullets are non-matching, all 36 CMPS scores are expected to be small with relatively the same values, resulting in a $\mathrm{\overline{CMPS}_{diff}}$ value close to 0.
For the example above, $\mathrm{\overline{CMPS}_{diff}} = 12.5 - 1.53 = 10.97$ <br>

@@

```{=tex}
\begin{align}
y_{kl} = \mu_k + e_{kl}
\end{align}
```
where $\mu_k$ is the true mean of group $k$ and $e_{kl}$ is a random effect of different observations.
Then we can define the sum of squares ratio $V$ as:
